---
title: "What We Know"
output:
  flexdashboard::flex_dashboard:
    orientation: rows
    logo: images/logo.jpg
    output_dir: docs
    
---

<style>
/* Edited CSS */

/* Set the font for the dasboard */

body {
  font-family: "Trebuchet MS", sans-serif;
}

h1, h2, h3, h4, h5, h6, .h1, .h2, .h3, .h4, .h5, .h6 {
  font-family: "Trebuchet MS", sans-serif;
  font-weight: 300;
  line-height: 1.1;
  color: #4A1D70;
}

/* Change the background colour of the sidebar to white */

#sidebar.section.sidebar {
  background-color: #ffffff;
}

/* Change the background colour of the navbar to white*/

.navbar.navbar-inverse {
  background-color: #ffffff;
  border-color: #4A1D70;
  color: #4A1D70;
}

/* This changes the horizontal line under the inactive tabs - I only wanted 
colour but had to use the whole code because it would not change */

.nav-tabs-custom>.nav-tabs {
    margin: 0;
    border-bottom: 0.1rem solid #4A1D70;
    color: #000000;
    font-size: 1rem;
    font-weight: 300;
    font-family: inherit;
    border-top-right-radius: 3px;
    border-top-left-radius: 3px;
}

/* Change the highlight colours around the tabs to match the C&C UK branding */

.nav-tabs-custom > .nav-tabs > li.active,
.nav-tabs-custom > .nav-tabs > li.active > a {
    border-top-color: #4A1D70;
    border-right-color: #4A1D70;
    border-left-color: #4A1D70;
    color: #000000;
}

</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE)

# Install and load packages
#install.packages("waffle", dependencies = TRUE) # for making waffle plots
#install.packages("showtext", dependencies = TRUE) # easier to use various types of fonts: https://github.com/yixuan/showtext

# Automatically use showtext to render text for future devices
#showtext::showtext_auto()
```


```{r country, include=FALSE}


```

Row {.tabset}
-------------------------------------

### Overview
This is a summary of what we know about inflammatory bowel disease in the UK, based on the most up-do-date, quality evidence generated from research.

The Knowledge & Information team have produced a range of materials explaining more about the conditions and relevant topics, which are available on the main website here: [All information about Crohn's and Colitis]( https://crohnsandcolitis.org.uk/info-support/information-about-crohns-and-colitis/all-information-about-crohns-and-colitis?parent=4107&page=1&tags=&category=&sort=).

#### Evidence & Insight: Key facts and resources

Country & Region: shows an overview of prevalence, diagnosis, surgery, care and lockdown. Country and region figures are included where available.

### Country & Region

A map with filters

### Demographics

Text and images of demographic data

### Prevalence & Incidence

What is the difference between the two?
Latest figures from the epidemiology report

### Treatment & Care

Perhaps graphic of timeline showing time to diagnosis

### Cost & Hospital Attendance

Stuff here

### Individual Health

### Impact on Life

### Family & Friends

### Life in Lockdown

### Crohn's & Colitis UK